final_project_draft

### 2022-04-18 draft.Rmd
April 18th graded before class commit. Got rid of some things but added new visualizations as well.

library(plotly)
options(scipen = 10)
## install.packages("ggpmisc")
library(ggpmisc)
```

## Top 25 Highest Political Donations by NFL Team Owners in 2016 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
high_donations <- pol_donations %>% filter(year == "2016" & League == "NFL") %>%
  mutate(amount = parse_number(Amount)) %>%
  arrange(desc(amount)) %>%
  mutate(Rank = rank(desc(amount))) %>%
  filter(Rank <= 25) %>%
  mutate(owner_ordered = fct_reorder(.f = Owner, .x = amount)) %>%
  mutate(party = fct_relevel(Party, c("Republican", "Democrat", "Bipartisan")))

@@

## Table of Owners Who Make the Most Donations
```{r}
library(knitr)
library(pander)
library(tidyverse)
library(kableExtra)

@@

## How Much Do They Donate? 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
owner_rank <- pol_donations %>% group_by(Owner, League) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

@@

@@

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())
```

## Examining Top Donator 
```{r}
library(ggthemes)
charles_johnson <- pol_donations %>% filter(Owner == "Charles Johnson") %>%
  filter(year == 2016 | year == 2018 | year == 2020)

cj_party <- charles_johnson %>% group_by(Party) %>%
  summarise(n = n()) %>%
  mutate(party = fct_reorder(.f = Party, .x = n)) %>%
   mutate(Party = fct_relevel(party, c("Republican", "Bipartisan, but mostly Republican",
                                         "Democrat")))

level_order2 <- factor(charles_johnson$Party, level = c('Republican', 'Democrat', 'Bipartisan, but mostly Republican'))

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d(option = "plasma") +
  labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
       x = " ",
       y = "Count of Donations") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20)))

cj_party2 <- cj_party %>% select(n, party)

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() + 
  annotate(geom = "table") +
  coord_flip()
```

## What Are Some of These Organizations? 
```{r}
organizations <- charles_johnson %>% group_by(Recipient, Party) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  filter(n >= 2)

@@

## Organizations Receiving Most Donations Across All Leagues 
```{r}
recipients <- pol_donations %>% group_by(Recipient, Party) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  filter(n >= 15) %>%
  ungroup() %>%
  mutate(recipient = fct_reorder(.f = Recipient, .x = n)) %>%
  mutate(Party = fct_relevel(Party, c("Bipartisan", "Republican", "Democrat")))

@@

## Potential questions:
## Who are the most recent top 10 billionaires: name v net worth ?

## look at average age of billionaires in general/maybe by country?: do billionaires tend to be very old or are there more billionaires on the younger side?

## Look at most prevalent industry of billionaires: mostly technology or something else?

## How many billionaires in each country: mostly capitalist or other economic systems?

@@

## Top 10 Billionaires coloured by industry (Forbes 2021 Billionaires)
```{r}
billionaires <- read_csv("data/Billionaire.csv")
billionaires

@@

## Forbes Billionaire 2021 2.0 Data Set
```{r}
forbes_billionaires <- read_csv("data/forbes_billionaires.csv")
forbes_billionaires

country <- forbes_billionaires %>% group_by(Country) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
country

forbes_billionaires_age <- forbes_billionaires %>%
  mutate(age = as.numeric(Age)) %>%
  select(age, everything())

countries_10 <- forbes_billionaires_age %>% filter(Country == "United States" |
           Country == "China" |
           Country == "India" |
           Country == "Germany" |
           Country == "Russia" |
           Country == "Hong Kong" |
           Country == "Brazil" |
           Country == "Canada" |
           Country == "United Kingdom" |
           Country == "Italy")

@@

check <- countries_10 %>% filter(Age < 25 | Age > 90)

filter <- countries_10 %>% filter(!is.na(age))
filter2 <- filter %>% group_by(Country) %>%
  summarise(Average = mean(age))

ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.2) +
  coord_flip() +
  geom_point(data = filter2, aes(y = Average, colour = "Mean Age"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country",
       caption = "The Red Points Indicate the Average Age of Billionaires From Each
       Country") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        legend.position = "none",
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) 
```

@@

ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
  geom_point() +
  coord_flip() +
  labs(x = "Education Level",
       y = "Net Worth")
```

@@

## Billionaires Age in Countries with most billionaires 
```{r}

ggplot(data = countries_10, aes(x = Country, y = Age)) +
  geom_point() +
  coord_flip() +
  geom_point(data = average_top10_countries, aes(y = Average, colour = "Average Billionaire Age")) +
  scale_colour_manual(values = c("Average Billionaire Age" = "red"))
```

## Blockbusters: A blockbuster is a Hollywood movie that's made with a large budget and big stars. A true blockbuster is extremely popular and brings in a lot of money (https://www.vocabulary.com/dictionary/blockbuster). 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
blockbusters <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/Blockbusters_2019-1977.csv")
blockbusters
```

## Blockbuster Ratings: 1977 to 2019
```{r, message = FALSE, warning = FALSE, echo = FALSE}
blockbusters %>% group_by(mpaa_rating) %>%
  summarise(n = n())

blockbusters1 <- blockbusters %>% filter(!is.na(mpaa_rating)) %>%
  rename(Film = 'film_title')

ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating,
                                          label = Film)) +
  geom_point() +
  facet_wrap(~mpaa_rating) +
  geom_smooth(se = FALSE, method = 'lm') +
  labs(y = "IMDB Rating",
       x = "Release Year",
       colour = "MPAA Rating",
       title = "Blockbuster Ratings: 1977 to 2019") +
  theme_hc() +
  scale_colour_brewer(palette = "Dark2") +
  theme(plot.title = element_text(family = "mono",
                                  face = "italic",
                                  margin = margin(t = 20, b = 20)),
        axis.ticks = element_blank(),
        axis.title = element_text(family = "mono",
                                  face = "italic"),
        axis.text = element_text(family = "mono"),
        legend.box.background = element_rect(),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "italic"),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.title.x = element_text(margin = margin(t = 20, b = 10)),
        strip.text = element_text(family = "mono",
                                  face = "bold"))

blockbusters %>% group_by(mpaa_rating) %>%
  summarise(n = n()) %>%
  filter(!is.na(mpaa_rating))
```

## Has the Budget for Blockbusters Increased Throughout Time? 
```{r}
ggplot(data = blockbusters, aes(x = release_year, y = film_budget, colour = release_year)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm", colour = "black") +
  labs(x = "Release Year",
       y = "Film Budget",
       title = "Has the Budget for Blockbuster Films Increased Throughout Time?",
       subtitle = "Film Budget for Blockbusters: 1977-2019") +
  theme_bw() +
  scale_colour_viridis_c() +
  theme(legend.position = "none",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50, b = 50)),
                                  vjust = 10),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     vjust = 5),
        axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
        axis.title.x = element_text(margin = margin(c(l = 20))),
        axis.title.y = element_text(margin = margin(c(t = 20, b = 20, r = 20)))) 
## need to add more to this visualization 
```

## Which American/Domestic Distributor Has Produced the Most Blockbusters 1977-2019
```{r}
blockbusters3 <- blockbusters %>% group_by(domestic_distributor) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  mutate(order = fct_reorder(.f = domestic_distributor, .x = n)) %>%
  filter(!n == 1)

ggplot(data = blockbusters3, aes(x = order, y = n, fill = order)) +
  geom_point() +
  geom_segment(aes(x = order, xend = order, y = 0, yend = n)) +
  coord_flip() +
  geom_label(data = blockbusters3, aes(label = n), show.legend = FALSE) +
  labs(x = "Amount of Films Produced",
       y = "Domestic Distributor",
       title = "Amount of Blockbusters Produced by Domestic Distributors: 1977-2019") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50)),
                                  vjust = 10),
        axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.text.y = element_text(face = "italic"),
        axis.ticks = element_blank(),
        axis.title.x = element_text(margin = margin(c(b = 20))),
        axis.title.y = element_text(margin = margin(c(t = 30, r = 30))))
```

## Work in Progress 
```{r}
blockbusters
interest <- blockbusters %>% mutate(rank = rank(desc(imdb_rating))) %>%
  select(rank, everything()) %>%
  arrange(rank) %>%
  slice(1:5) %>%
  mutate(film_title = fct_recode(film_title, 
                                 LOTR_The_Return_Of_The_King = "The Lord of the Rings: The Return of the King",
                                 LOTR_Fellowship_Of_The_Ring = "The Lord of the Rings: The Fellowship of the Ring"))
interest

interest2 <- blockbusters %>% mutate(rank = rank(imdb_rating)) %>%
  select(rank, everything()) %>%
  arrange(rank) %>%
  slice(1:5)
interest2

library(ggrepel)
ggplot(data = interest, aes(x = release_year, y = domestic_gross)) +
  geom_point(aes(colour = imdb_rating)) +
  geom_label_repel(data = interest, aes(label = film_title)) +
  geom_point(data = interest2, aes(x = release_year, y = domestic_gross, colour = imdb_rating)) +
  geom_label_repel(data = interest2, aes(label = film_title))
```

## History of Rock
```{r, message = FALSE, warning = FALSE, echo = FALSE}
library(tidyverse)
history_of_rock <- read_csv("/Users/lilykasperek/Desktop/my-website/content/post/2022-03-22-first-post/history-of-rock-spotify.csv")
history_of_rock
```

## Most Popular Nirvana Songs 
```{r}
history_of_rock %>% group_by(artist) %>%
  summarise(n = n()) %>% arrange(desc(n))

nirvana <- history_of_rock %>% rename(Popularity = 'popularity') %>%
  filter(artist == "Nirvana") %>% arrange(desc(Popularity)) %>%
  mutate(order = fct_reorder(.f = name, .x = Popularity)) %>%
  rename(Release_Date = 'release_date')

nirvana %>% select(order, everything())

plot3 <- ggplot(data = nirvana, aes(x = order, y = Popularity, label = Popularity, colour = Popularity)) +
  geom_point() +
  geom_segment(aes(x = order, xend = order, y = 0, yend = Popularity)) +
  coord_flip() +
  labs(title = "Most Popular Nirvana Songs: 1991-2018",
       colour = "Popularity", 
       x = " ",
       y = " ") +
  theme_bw() +
  scale_colour_viridis_b() +
  theme(legend.position = "none")

ggplotly(plot3, tooltip = "label")
```

## Trying to Make Density Ridges Plot 
```{r}
## install.packages("ggridges")
library(ggridges)

nirvana_small <- nirvana %>% slice(1:5) %>%
  mutate(order = fct_reorder(.f = name, .x = valence))
ggplot(data = nirvana_small, aes(x = order, y = valence)) +
  geom_density_ridges() +
  coord_flip() +
  labs(x = "Title",
       y = "Valence")
```

## Works in Progress - Simple Visualizations
```{r}
nirvana_line <- nirvana %>% rename(Title = 'name')
plot10 <- ggplot(data = nirvana_line, aes(x = Release_Date, y = Popularity, label = Title)) +
  geom_line() +
  geom_point(colour = "darkolivegreen") +
  labs(x = "Release Date",
       y = "Popularity",
       title = "Comparing Popularity by Release Date") +
  theme_bw() +
  theme(legend.position = "none")

ggplotly(plot10, tooltip = "label")

table <- history_of_rock %>% group_by(artist) %>%
  summarise(mean = mean(popularity)) %>%
  arrange(desc(mean)) %>%
  slice(1:10)

top10 <- history_of_rock %>% arrange(desc(popularity)) %>% slice(1:10)
```

## Unemployment Data Set
```{r}
library(lubridate)
unemployment <- read_csv("data/unemployment_data_us.csv")
ggplot(data = unemployment, aes(x = Date, y = Professional_Degree)) +
  geom_point()
```

>>>>

library(plotly)
options(scipen = 10)
library(ggpmisc)
library(ggrepel)
```

## Questions: What were the highest 25 Political Donations made by NFL team owners in 2016? Were the majority of these donations affiliated with a certain party? How much influence could NFL team owners have on elections? Is there any gender that dominates?
```{r, message = FALSE, warning = FALSE, echo = FALSE}
high_donations <- pol_donations %>% filter(year == "2016" & League == "NFL") %>%
  mutate(amount = parse_number(Amount)) %>%
  arrange(desc(amount)) %>%
  mutate(Rank = rank(desc(amount))) %>%
  filter(Rank <= 25) %>%
  mutate(owner_ordered = fct_reorder(.f = Owner, .x = amount)) %>%
  mutate(party = fct_relevel(Party, c("Republican", "Democrat", "Bipartisan")))

@@

## Questions: Which owners, across all leagues, have made the most political donations from this data set? How many have they made? Is there a certain gender that dominates? 
```{r}
library(knitr)
library(pander)
library(tidyverse)
library(kableExtra)

@@

## Questions: How much money was spent for these donations? Do these donations tend to be made to the same party for each owner or do they vary? What is the total sum of the donations made by these individuals? What is the average amount per donation? 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
owner_rank <- pol_donations %>% group_by(Owner, League) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

@@

frequent %>% group_by(Party) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

average_donation <- frequent %>% group_by(Owner) %>%
  mutate(mean = mean(amount))
average_donation

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  geom_point(data = average_donation, aes(x = mean, colour = "Mean")) +
  scale_colour_manual(values = c("Mean" = "Red"))

@@

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 5),
        legend.text = element_text(family = "mono",
                                   size = 5),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9),
        legend.box.background = element_rect())

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations")) +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
  scale_colour_manual(values = c("Mean Donations" = "red")) +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations")) +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_viridis_d() +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())

  scale_fill_discrete(limits = c("Republican", "Democrat", 
                                      "Bipartisan, but mostly Republican", 
                                      "Bipartisan", "N/A",
                                      "Bipartisan, but mostly Democratic",
                                      "Independent", 
                                      "Mean Donations"))

frequent %>% mutate(party = fct_relevel(Party, c("Republican", "Democrat", 
                                      "Bipartisan, but mostly Republican", 
                                      "Bipartisan", "N/A",
                                      "Bipartisan, but mostly Democratic",
                                      "Independent", 
                                      "Mean Donations")))

sum_donations <- frequent %>% group_by(Owner) %>%
  summarise(sum = sum(amount)) %>%
  rename(Sum = 'sum') %>%
  arrange(desc(Sum))
sum_donations

pandoc.table(sum_donations, style = "grid")
```

## Questions: How many donations, out of the 213 made by Charles Johnson, were made to which political parties? 
```{r}
library(ggthemes)
charles_johnson <- pol_donations %>% filter(Owner == "Charles Johnson") %>%
  filter(year == 2016 | year == 2018 | year == 2020)

 cj_party <- charles_johnson %>% group_by(Party) %>%
  summarise(n = n()) %>%
  mutate(party = fct_reorder(.f = Party, .x = n)) %>%
   mutate(Party = fct_relevel(party, c("Democrat", "Bipartisan, but mostly Republican", "Republican")))

level_order2 <- factor(charles_johnson$Party, level = c('Democrat', 'Bipartisan, but mostly Republican', 'Republican'))

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  scale_fill_viridis_d(option = "inferno") +
  labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
       x = " ",
       y = " ") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20)),
        axis.title.y = element_text(family = "mono",
                                    margin = margin(t = 20, b = 20, r = 20)))

table_cjparty <- cj_party %>% arrange(desc(n)) %>%
  select(Party, n) %>%
  rename(Count = 'n')
pandoc.table(table_cjparty)
```

## Question: As we can see, most of the donations made by Charles Johnson were affiliated with the Republican party. What were some of these organizations and how many donations did Charles Johnson make to each of these organizations? 
```{r}
organizations <- charles_johnson %>% group_by(Recipient, Party) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  filter(n >= 2)

@@

## Questions: What are some organizations that seem to be recieving the most donations across all owners and leagues? What political party are these organizations affiliated with? 
```{r}
recipients <- pol_donations %>% group_by(Recipient, Party) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  filter(n >= 15) %>%
  ungroup() %>%
  mutate(recipient = fct_reorder(.f = Recipient, .x = n)) %>%
  mutate(Party = fct_relevel(Party, c("Bipartisan", "Republican", "Democrat")))

@@

@@

## Questions: Who were the billionaires with the top 10 highest net worths on the 2021 Forbes Billionaires List? How much are their net worths? What industry do they work in? Does any industry dominate the others? 
```{r}
billionaires <- read_csv("data/Billionaire.csv")
billionaires
forbes_billionaires <- read_csv("data/forbes_billionaires.csv")
forbes_billionaires

@@

## Questions: What is the average age of the billionaires from the 10 countries with the most billionaires? Is there a pattern or do the averages widely differ? Are there any interesting outliers? 
```{r}
forbes_billionaires_age <- forbes_billionaires %>%
  mutate(age = as.numeric(Age)) %>%
  select(age, everything())

countries_10 <- forbes_billionaires_age %>% filter(Country == "United States" |
           Country == "China" |
           Country == "India" |
           Country == "Germany" |
           Country == "Russia" |
           Country == "Hong Kong" |
           Country == "Brazil" |
           Country == "Canada" |
           Country == "United Kingdom" |
           Country == "Italy") 
countries_10

@@

check <- countries_10 %>% filter(age < 25 | age > 97)
check

filter <- countries_10 %>% filter(!is.na(age))
filter
filter2 <- filter %>% group_by(Country) %>%
  summarise(Average = mean(age)) %>%
  mutate(order = fct_reorder(.f = Country, .x = Average))
filter2

ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country",
       caption = "The Red Points Indicate the Average Age of Billionaires From Each
       Country") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        legend.position = "none",
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) +
  geom_label_repel(data = check, aes(label = age, family = "mono"))
```

## Average net worth per industry 
```{r}
forbes_billionaires %>% group_by(Country) %>%
  summarise(avg = mean(NetWorth))

usa_df <- billionaires %>% filter(Country == "United States") %>% mutate(networth = parse_number(NetWorth)) 
usa_df

usa_df %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

usa_avg_df <- usa_df %>%
   summarise(avg = mean(networth))
usa_avg_df

above_or_below_us <- usa_df %>% mutate(avg = mean(networth)) %>%
  mutate(above_avg = if_else(networth > 6.08,
                                      true = "ABOVE AVG",
                                      false = "BELOW AVG")) %>%
  filter(Industry == "Fashion & Retail") %>%
  mutate(order = fct_reorder(.f = Name, .x = networth))
above_or_below_us

ggplot(data = above_or_below_us, aes(x = order, y = networth, colour = above_avg)) +
  geom_segment(aes(x = order, xend = order, y = avg, yend = networth)) +
  geom_point() +
  coord_flip() +
  labs(x = "Name",
      y = "Net Worth",
      colour = "Average") +
  theme(axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono"),
        axis.ticks = element_blank())
```

## Questions: How many billionaires are there from the top 30 countries on the list? Do developed democracies have the most billionaires on the list?
```{r}
country <- forbes_billionaires %>% group_by(Country) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

country_30 <- country %>% slice(1:30) %>%
  mutate(order = fct_reorder(.f = Country, .x = n))
country_30

ggplot(data = country_30, aes(x = order, y = n)) +
  geom_point(colour = "orange") +
  geom_segment(aes(x = order, xend = order, y = 0, yend = n), colour = "blue", linetype = "dotdash") +
  coord_flip() +
  theme_light() +
  theme(axis.ticks.x = element_blank()) +
  labs(x = "Country", 
       y = "Count of Billionaires",
       title = "How Many Billionaires Are There From the Top 30 Countries?") +
  theme(plot.title = element_text(family = "mono"),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"))
```

@@

ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  labs(x = "Education Level",
       y = "Net Worth")

ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
  geom_jitter(alpha = 0.4) +
  coord_flip() +
  labs(x = "Education Level",
       y = "Net Worth")
```

@@
